---
title: ""
output: 
  html_document:
    css: style.css
    toc: false
    includes:
      #in_header: footer.html
      #before_body: footer.html
     # after_body: footer.html
---

&nbsp;
&nbsp;
<left> <h1> <strong> Interactive Visualizations </strong></h1> </left>

---

This is just a compendium of the most interesting visualizations that I have done while I was working as a data scientist, most of them where modified to protect data privacy (Work in progress).

The images here are not those that I am interested to show (<strong> Web Page under construction </strong>)

&nbsp;
&nbsp;

&nbsp;
&nbsp;


---

<left> <h4> <strong> Houses for rent in the comunity of  Madrid </strong></h4> </left>

```{r echo=FALSE, fig.height=4, fig.width=10, message=FALSE, warning=FALSE}


#shiny::includeHTML("./animations/MAPA.html")



# library("rgdal")
# library("rgeos")
# library("data.table")
# suppressWarnings(library(leaflet))
# 
# 
# #------------------------------------------------------------------------------------
# # Load the output area shapefiles
# data.shape <- readOGR('/home/erika/Dropbox/GIT/MARKDOWN/restore/data/map/sscc_2016.shp', verbose = F)
# 
# load("data/indicadores.SSCC.RData")
# Census.Data <- as.data.table(indicadores.SSCC)
# Census.Data <- Census.Data[substr(SSCC, 1,2) == 28, ]
# 
# Census.Data <- as.data.frame(Census.Data)
# pal  <- colorNumeric(palette = 'Blues', domain = c(min(Census.Data[, 335]), max(Census.Data[, 335])))
# mapa <- leaflet() %>%
#   addPolygons(data = data.shape[data.shape$CUSEC %in% Census.Data[,1], ],
#               weight = 1,
#               color = '#000000',
#               fillColor = pal(as.numeric(Census.Data[,335])),
#               fillOpacity = 0.6,
#               popup = ~paste0("<b> SSCC: </b>", CUSEC, "<br>",
#                               "<b> Municipality: </b>", NMUN, "<br>",
#                               "<b> Num. of houses for rent: </b>", Census.Data[, 335], "<br>")) %>%
#   addProviderTiles('OpenStreetMap.Mapnik') %>%
#   addLegend("bottomright", pal = pal, values = (as.numeric(Census.Data[,335])),
#             title = "Houses for rent",
#             opacity = 0.6 )
# 
# mapa

``` 
   
  

\
\

&nbsp;

--- 

&nbsp;

<left> <h4> <strong> Number of devices connected to a Wi-Fi network by day and hour </strong></h4> </left>



```{r echo=FALSE, message=FALSE}
require(dplyr)
require(highcharter)
require(htmlwidgets)

source('src/functions_highchart.R')
load('/home/erika/Dropbox/GIT/MARKDOWN/data/dat.purple.dup.RData')


dat.aux.dup.x     <- dat.purple.dup[order(SEEN), ][, MEAN_FREQ_HOUR := round(mean(FREQ_DAY_HOUR),2), by = HOUR][, .(DAY, HOUR, FREQ_DAY_HOUR, MEAN_FREQ_HOUR, MONTH, YEAR)][, KEY := paste0(DAY, '-', HOUR)]
dat.aux.dup.x     <- dat.aux.dup.x[!duplicated(KEY)][order(HOUR, FREQ_DAY_HOUR), ]
dat.aux.dup.x     <- dat.aux.dup.x[, TITLE := 'DAY'][, TITLE2 := 'DAILY MEAN'] 
dat.aux.dup.x     <- dat.aux.dup.x[, .(DAY, HOUR, FREQ_DAY_HOUR,  MEAN_FREQ_HOUR, TITLE, TITLE2, MONTH, YEAR)] 
dat.aux.dup.x.dup <- dat.aux.dup.x[!duplicated(HOUR),][order(HOUR), ]
names(dat.aux.dup.x)     <- c('Z', 'X', 'Y', 'Y2', 'TITLE', 'TITLE2', 'W', 'H')
dat.aux.dup.x.dup <- dat.aux.dup.x.dup[, DAY := NA]
names(dat.aux.dup.x.dup) <-  c('Z', 'X', 'Y', 'Y2', 'TITLE', 'TITLE2', 'W', 'H')

#plot the graphs
graph_points_lines(dat.aux.dup.x, dat.aux.dup.x.dup, xlabel = "Hour", ylabel = "Number of dispositives connected", ylegend ='Frequency')

dat.aux.dup.x <- dat.aux.dup.x[order(Z), ][!duplicated(Z), ][, X := Z][, Z := NULL]
dt <- dat.aux.dup.x
graph_lines(dt, xlabel = "Day", ylabel = "Number of dispositives connected", ylegend ='Frequency', zlegend ='Day')

 ``` 


---

   
   

